---
title: "GMCSF_reanalysis"
author: "Melissa"
date: "28/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Functions:
```{r}
vln=function(SeuratObject, Genes, Reference){
  p <-VlnPlot(SeuratObject, Genes, pt.size = 0, combine = F , group.by = "celltype")
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] +NoLegend()+
  stat_summary(fun= median, geom='point', size = 5, colour = "black", shape = 95) +
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = Reference)}
   res=cowplot::plot_grid(plotlist = p, ncol = 3)
  return(res)
}
```

```{r}
preprocess= function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "mvp", nfeatures = 3000)
    x= ScaleData(x)
    x= RunPCA(x)
     x <- FindNeighbors(x, dims = 1:20)
    x <- FindClusters(x, resolution = 0.4, dims=1:20)
   x<- RunUMAP(x, dims = 1:20)
    }
```

```{r}
library(Seurat)
seur= Read10X("/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/GMCSF/")
seurd=CreateSeuratObject(seur,  min.genes = 100, project = "GMCSF")
seurd[["percent.mito"]] <- PercentageFeatureSet(seurd, pattern = "^MT-")
VlnPlot(seurd, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
## low.thresholds = c(20000, -Inf,3500), high.thresholds = c(90000, 0.30,8000)
seurd=subset(seurd, subset  = nFeature_RNA < 8000 & nCount_RNA <90000 & percent.mito <30)
seurd= subset(seurd, subset  = nFeature_RNA > 3500 & nCount_RNA >20000)
VlnPlot(seurd, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
seurd=SubsetData(seurd, ident.remove = 4)
seurd=DietSeurat(seurd)
```

```{r}
seurd= preprocess(seurd)
```

```{r}
seurd= preprocess(seurd)
#use MAGIC on the expression values
library(Rmagic)
td=t(seurd@assays$RNA@data)
td=as.matrix(td)

genes=c("BCL6","PDCD1", "CXCR5","ICOS","IL21","TBX21","GATA3","RORC","FOXP3","MAF","CCR6","CXCR3","IFNG","TNF","IL4","IL13","IL9","IL17A","CXCL13","IL5", "IL13", "CXCL13","TNFA", "IL17F", "FOXP3", "CD27", "IL32")
genes=append(genes, VariableFeatures(seurd))
####
DefaultAssay(seurd)= "RNA"
mobj=magic(td, genes=rownames(seurd),k=20, t="auto", n.jobs = -2)
magic.res=mobj$result
library(Seurat)
seurd[['imputed']] <- CreateAssayObject(data = as.matrix(x = t(magic.res)))

DefaultAssay(seurd)="imputed"
library(ggplot2)
library(viridis)
tfh=list(c("BCL6","PDCD1", "CXCR5","IL21"))
th1= list(c("TNF","IFNG","TBX21"))
th2=list(c("IL4", "IL5","GATA3"))
tfh1=list(c("BCL6","PDCD1", "CXCR5","IL21", "TNF","IFNG","TBX21"))
th17=list(c("IL17A", "IL17F", "RORC"))
gmcsf=seurd
```

KEPT:
```{r}
seurd=AddModuleScore(seurd, features = tfh, name="TFH_signature", nbin = 10, ctrl = 4)
seurd=AddModuleScore(seurd, features = th1, name="TH1_signature",ctrl = 10,nbin = 4)
seurd=AddModuleScore(seurd, features = th2, name="TH2_signature",ctrl.size = 4,nbin = 10)
seurd=AddModuleScore(seurd, features = tfh1, name="TFH1_signature",ctrl.size = 10,nbin = 4)
seurd=AddModuleScore(seurd, features = th17, name="TH17_signature",ctrl.size = 10,nbin = 4)
VlnPlot(seurd, c("TFH_signature1" , "TH1_signature1" , "TH2_signature1"), pt.size = 0)
saveRDS(seurd, "/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/Analysis_GMCSF/GMCSF.Rds")
```

```{r}
library(gtable)
library(gridExtra)
library(grid)
nbr=as.data.frame( table(seurd$seurat_clusters))
colnames(nbr)=c("cluser", "NumberCells")                 
g <- tableGrob(nbr, rows = NULL)
g <- gtable_add_grob(g,
        grobs = rectGrob(gp = gpar(fill = NA, lwd = 2)),
        t = 1, l = 1, r = ncol(g))
grid.draw(g)
```

```{r}
library(viridis)
library(ggpubr)
A=FeaturePlot(seurd, "TH1_signature1")+NoAxes()+scale_color_viridis(option = "B")
B= FeaturePlot(seurd, "TH2_signature1")+NoAxes()+scale_color_viridis(option = "B")
C=FeaturePlot(seurd, "TH17_signature1")+NoAxes()+scale_color_viridis(limits=c(-0.0011,0.01),option = "B")
D=FeaturePlot(seurd, "TFH_signature1")+NoAxes()+scale_color_viridis(option = "B")
ggarrange(A,B,C,D, ncol = 4)
```

```{r}
FeatureScatter(seurd, "TFH_signature1", "TH1_signature1")
FeatureScatter(seurd, "TFH_signature1", "TFH1_signature1")
FeatureScatter(seurd, "TH2_signature1", "TFH_signature1")
FeatureScatter(seurd, "TH2_signature1", "TFH1_signature1")
FeatureScatter(seurd, "TH2_signature1", "TH1_signature1")
```

create cell type column:
```{r}
celltype=c("Tfh1", "Tfh", "Th2","Tfh1")
names(celltype)=levels(seurd)
seurd=RenameIdents(seurd, celltype)
seurd$celltype=Idents(seurd)
DimPlot(seurd)
```

Estimate the fraction of cells:
```{r}
nbr=as.data.frame(table(seurd$celltype))
colnames(nbr)=c("CellType", "NumberCells")
nbr$Fraction=nbr$NumberCells/100
nbr
library(ggplot2)
library(scales)
# Bar plot
blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )
bp<- ggplot(nbr, aes(x="", y=Fraction, fill=CellType))+
geom_bar(width = 1, stat = "identity")  + coord_polar("y", start=0) +
  blank_theme+
  theme(axis.text.x=element_blank())+
  geom_text(aes( y = Fraction/3 +c(0, cumsum(Fraction-4)[-length(Fraction)]) , 
                label = percent(Fraction/100)), size=5)
```

Check the boxplot distribution for each module within each cell type
```{r}
VlnPlot(seurd, c("TH1_signature1","TH2_signature1","TFH_signature1", "TFH1_signature1"), ncol = 2)

FeatureScatter(seurd, "TFH_signature1", "TFH1_signature1")
FeatureScatter(seurd, "TH2_signature1","TFH_signature1")
```

```{r}
p=FeaturePlot(seurd, c("BCL6", "PDCD1","CXCR5","IL21"), combine = F)
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] +
    NoAxes()+scale_color_viridis(option = "B") }
cowplot::plot_grid(plotlist = p, ncol = 4)
```

Create another column with Th1:
```{r}
seurd$CT= gsub("Tfh1", "Th1", seurd$celltype)

nbr=as.data.frame(table(seurd$CT))
colnames(nbr)=c("CellType", "NumberCells")

ggplot(nbr, aes(x="", y=NumberCells, fill=CellType))+
geom_bar(width = 1, stat = "identity")  + coord_polar("y", start=0) +
  blank_theme+
  theme(axis.text.x=element_blank())+
  geom_text(aes( y = NumberCells/3 +c(0, cumsum(NumberCells-4)[-length(NumberCells)]) , 
                label = paste(NumberCells/100, "%")), size=5)
```

```{r}
vln(seurd, c("BCL6", "PDCD1","CXCR5","IL21"), "Tfh1")
vln(seurd, c("TNF", "IFNG","TBX21"), "Tfh1")
vln(seurd, c("IL4","IL13","GATA3"), "Th2")
vln(seurd,c("IL17A", "IL17F","RORC") )
vln(seurd, c("TH1_signature1","TH2_signature1","TFH_signature1", "TFH1_signature1"), "Tfh1")



p <-VlnPlot(seurd, c("IL17A", "IL17F","RORC"), pt.size = 0, combine = F , group.by = "celltype")
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] +NoLegend()+
  stat_summary(fun= median, geom='point', size = 5, colour = "black", shape = 95) +
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "Th2")}
cowplot::plot_grid(plotlist = p, ncol = 3)
```



TH1, TH2, TH17 separate genes:
```{r}
genes=c("TNF", "IFNG","TBX21")
genes= c("IL4","IL13","GATA3")
genes=c("IL17A", "IL17F","RORC")
p=FeaturePlot(seurd,genes , combine = F)
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] +
    NoAxes()+scale_color_viridis(option = "B", limits=c(0,0.02)) }
cowplot::plot_grid(plotlist = p, ncol = 3)
```

```{r}
p=FeaturePlot(seurd,c("TH1_signature1","TH2_signature1","TH17_signature1", "TFH_signature1") , combine = F)
for(i in 1:length(p)) {
  p[[i]] <- p[[i]] +
    NoAxes()+scale_color_viridis(option = "B") }
cowplot::plot_grid(plotlist = p, ncol = 4)
```



Correlation Matrix:
```{r}
g=c("TNF", "IFNG" ,"TBX21","IL4","IL13","GATA3","IL17A", "IL17F","RORC","BCL6", "PDCD1","CXCR5","IL21")

pheatmap::pheatmap(cor(magic.res[,which(colnames(magic.res) %in% g)]))
```
 Save the gmcsf dataset:
```{r}
saveRDS(seurd, "/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/Analysis_GMCSF/GMCSF_finalSeuratObject.Rds")
```
 

################# LPS ########################
```{r}
library(Seurat)
lps= Read10X("/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/LPS/")
lps=CreateSeuratObject(lps,  min.genes = 100, project = "GMCSF")
lps[["percent.mito"]] <- PercentageFeatureSet(lps, pattern = "^MT-")
VlnPlot(lps, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
## low.thresholds = c(20000, -Inf,3500), high.thresholds = c(90000, 0.30,8000)
lps=subset(lps, subset  = nFeature_RNA < 8000 & nCount_RNA <90000 & percent.mito <30)
VlnPlot(lps, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
##
lps= preprocess(lps)
DimPlot(lps)+NoAxes()
```

#use MAGIC on the expression values
```{r}
library(Rmagic)
ld=t(lps@assays$RNA@data)
ld=as.matrix(ld)
DefaultAssay(lps)= "RNA"
lobj=magic(ld, genes=rownames(lps),k=20, t="auto", n.jobs = -2)
magic.resL=lobj$result

library(Seurat)
lps[['imputed']] <- CreateAssayObject(data = as.matrix(x = t(magic.resL)))

DefaultAssay(lps)="imputed"
library(ggplot2)
library(viridis)
tfh=list(c("BCL6","PDCD1", "CXCR5","IL21"))
th1= list(c("TNF","IFNG","TBX21"))
th2=list(c("IL4", "IL5","GATA3"))
tfh1=list(c("BCL6","PDCD1", "CXCR5","IL21", "TNF","IFNG","TBX21"))
th17=list(c("IL17A", "IL17F", "RORC"))
```

Save the LPS dataset:
```{r}
saveRDS(lps, "/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/Analysis_LPS/LPS_final.Rds")
```

##############################################################
########### MEDIUM ######################### 

```{r}
library(Seurat)
cnt= Read10X("/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/Naive/")
cnt=CreateSeuratObject(cnt,  min.genes = 100, project = "MEDIUM")
cnt[["percent.mito"]] <- PercentageFeatureSet(cnt, pattern = "^MT-")
###
VlnPlot(cnt, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
cnt=subset(cnt, subset  = nFeature_RNA < 2000 & nCount_RNA <10000 & percent.mito <30)
VlnPlot(cnt, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
##
cnt= preprocess(cnt)
DimPlot(cnt)+NoAxes()
```

```{r}
library(Rmagic)
cd=t(cnt@assays$RNA@data)
cd=as.matrix(cd)
DefaultAssay(cnt)= "RNA"
cobj=magic(cd, genes=rownames(cnt),k=20, t="auto", n.jobs = -1)
magic.resC=cobj$result
library(Seurat)
cnt[['imputed']] <- CreateAssayObject(data = as.matrix(x = t(magic.resC)))

DefaultAssay(cnt)="imputed"
library(ggplot2)
library(viridis)
tfh=list(c("BCL6","PDCD1", "CXCR5","IL21"))
th1= list(c("TNF","IFNG","TBX21"))
th2=list(c("IL4", "IL5","GATA3"))
tfh1=list(c("BCL6","PDCD1", "CXCR5","IL21", "TNF","IFNG","TBX21"))
th17=list(c("IL17A", "IL17F", "RORC"))
```

Save the MEDIUM dataset
```{r}
saveRDS(cnt, "/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/Analysis_MEDIUM/Medium.Rds")
```

###########################################################################
##########Downstream Analyses : common for the three datasets #############
Plot the genes and keep the same scale as in GMCSF:
```{r}
summary(magic.res[,"BCL6"])
summary(magic.res[,"PDCD1"])
summary(magic.res[,"CXCR5"])
summary(magic.res[,"IL21"])
```

```{r}
a=FeaturePlot(lps, "BCL6") +
    NoAxes()+ NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.05743))
b=FeaturePlot(lps, "PDCD1") +
    NoAxes()+NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.10180))
c=FeaturePlot(lps, "CXCR5") +
    NoAxes()+NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.05761))
d=FeaturePlot(lps, "IL21") +
    NoAxes()+NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.09318))
```

```{r}
DefaultAssay(cnt)="imputed"
a=FeaturePlot(cnt, "BCL6") +
    NoAxes()+ NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.05743))
b=FeaturePlot(cnt, "PDCD1") +
    NoAxes()+ NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.10180))
c=FeaturePlot(cnt, "CXCR5") +
    NoAxes()+ NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.05761))
d=FeaturePlot(cnt, "IL21") +
    NoAxes()+ NoLegend()+scale_color_viridis(option = "B", limits=c(0,0.09318))
ggarrange(a,b,c,d, ncol = 4)
```

```{r}
lps=AddModuleScore(lps, features = tfh, name="TFH_signature", ctrl = 4, nbin = 10)
VlnPlot(lps, c("TFH_signature1"))
##
cnt=AddModuleScore(cnt, features = tfh, name="TFH_signature", ctrl = 4, nbin = 10)
VlnPlot(cnt, c("TFH_signature1"))
##
A=FeaturePlot(cnt, "TFH_signature1")+NoAxes()+NoLegend()+scale_color_viridis(option = "B",limits=c(-0.012368,0.035435))

B=FeaturePlot(lps, "TFH_signature1")+NoAxes()+NoLegend()+scale_color_viridis(option = "B", limits=c(-0.012368,0.035435))

C=FeaturePlot(seurd, "TFH_signature1")+NoAxes()+scale_color_viridis(option = "B", limits=c(-0.012368,0.035435))
ggarrange(A,B,C, ncol = 3)
```

Save the gmcsf dataset:
```{r}
saveRDS(cnt, "/Users/equipe.soumelis/Desktop/Projects/scRNAseq_DC_Tfh/")
```



