---
title: "TFH1_COVID19"
author: "Melissa"
date: "04/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Seurat)
sdata= Read10X("/Users/equipe.soumelis/Desktop/Projects/scRNAseqCOVID_datasets/GSE149689_Immunophenotyping of COVID-19 and InfluenzaSevere COVID-19")
s=CreateSeuratObject(sdata) #, min.cells = 10, min.features = 50
```

Add information regarding the sample of origin:

```{r}
library(readxl)
ms1 <- read_excel("/Users/equipe.soumelis/Desktop/Projects/scRNAseqCOVID_datasets/GSE149689_Immunophenotyping of COVID-19 and InfluenzaSevere COVID-19/Supp files/Table_S1 (1).xlsx")
##
ms1$`Sample ID`=gsub(" ","",ms1$`Sample ID`)
ms1$`Sample ID`=gsub("Normal","HD",ms1$`Sample ID`)
cn=colnames(s)
library(stringr)
cn=cn %>% str_match_all("[0-9]+") %>% unlist %>% as.numeric
####
s$index=cn
Idents(s)="index"
##
sid=c( "1"= "nCoV1", "2"= "nCoV2", "3"= "Flu1", "4"= "Flu2", "5"= "HD1","6"= "Flu3","7"= "Flu4", "8"="Flu5", "9"="nCoV3", "10"= "nCoV4", "11"= "nCoV5", "12"="nCoV6", "13"="HD2", "14"="HD3", "15"="nCoV7","16"="nCoV8", "17"="nCoV9", "18"="nCoV10", "19"="HD4", "20"="nCoV11")
s=RenameIdents(s, sid)
s$sampleID=Idents(s)
##
ms1$`Disease group`=gsub("-19","", ms1$`Disease group`)
ms1=as.data.frame(ms1)
rownames(ms1)= ms1$`Sample ID`
Idents(s)="sampleID"
ms1=ms1[levels(s),]
all(levels(Idents(s))== ms1$`Sample ID`)
###
dg= ms1$`Disease group`
names(dg)=levels(s)
s=RenameIdents(s, dg)
s$DiseaseGroup= Idents(s)
```

```{r}
##
ms1[10,2]= "F5"
ms1[16,2]= "C6"
ms1[18,2]= "C7"
##
Idents(s)="sampleID"
pid= ms1$`Patient ID`
names(pid)=levels(s)
s=RenameIdents(s, pid)
s$patientID= Idents(s)
```

```{r}
s[["percent.mito"]] <- PercentageFeatureSet(s, pattern = "^MT-")

VlnPlot(s, c("nCount_RNA", "nFeature_RNA","percent.mito"))
s=subset(s, percent.mito < 30)
s=subset(s, nFeature_RNA > 500)
s=subset(s, nCount_RNA > 1000)
preprocess= function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 3000)
    x= ScaleData(x)}
    #x= RunPCA(x, features = VariableFeatures(object = x))
    # x <- FindNeighbors(x, dims = 1:30)
    #x <- FindClusters(x, resolution = 1.0)
   #x<- RunUMAP(x, dims = 1:30)}

s=preprocess(s)
saveRDS(s, "/Users/equipe.soumelis/Desktop/Projects/scRNAseqCOVID_datasets/GSE149689_Immunophenotyping of COVID-19 and InfluenzaSevere COVID-19/Analysis/seurat_AllFiltered.Rds" )
##
s=readRDS("/Users/equipe.soumelis/Desktop/Projects/scRNAseqCOVID_datasets/GSE149689_Immunophenotyping of COVID-19 and InfluenzaSevere COVID-19/Analysis/seurat_AllFiltered.Rds")
```

```{r}
tcd4= subset(s, PTPRC>0.3 & CD3E > 0.3 & CD4 > 0.3  )
tcd4= DietSeurat(tcd4)

preprocess= function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 3000)
    x= ScaleData(x)
    x= RunPCA(x, features = VariableFeatures(object = x))
     x <- FindNeighbors(x, dims = 1:30)
    x <- FindClusters(x, resolution = 0.8)
   x<- RunUMAP(x, dims = 1:30)}
tcd4= preprocess(tcd4)
##
p=FeaturePlot(tcd4, c("PTPRC","CD4"))
ggsave(filename=paste0("/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_17november/FP_CD45_CD4_",Sys.Date() ,".png"), plot=p, device="png", height=5, width=8, units="in", dpi=500)
```

Construct TFH signature:
tfh1=c("BCL6","PDCD1", "CXCR5","IL21", "TNF","IFNG","TBX21")
```{r}
tfh=list(c("BCL6","PDCD1", "CXCR5","IL21", "ICOS"))
tcd4= AddModuleScore(tcd4, features = tfh, name = "TFHSignature", nbin = 100, ctrl = 200)
##
library(RColorBrewer)
library(ggpubr)
getPalette = colorRampPalette(brewer.pal(9, "Set1"))

p1=DimPlot(tcd4, cols = getPalette(length(unique(tcd4$DiseaseGroup))), group.by = "DiseaseGroup")
ggsave(filename="Umap_CD4_DG.png", plot=p1, device="png",
        height=5, width=6, units="in", dpi=500)
###
p1=VlnPlot(tcd4, group.by = "sampleID", "TFHSignature1", cols = getPalette(length(unique(tcd4$sampleID))) )
ggsave(filename="VLN_CD4_SID_TFH.png", plot=p1, device="png",
        height=8, width=8, units="in", dpi=500)
##
p2=VlnPlot(tcd4, group.by = "DiseaseGroup", "TFHSignature1", cols = getPalette(length(unique(tcd4$DiseaseGroup))) )
#
ggsave(filename="VLN_CD4_DG_TFH.png", plot=p2, device="png",
        height=8, width=8, units="in", dpi=500)
#######
p2=VlnPlot(cdc, group.by = "DiseaseGroup", "DC2dc1", cols = getPalette(length(unique(cdc$DiseaseGroup))) )
#
ggsave(filename="VLN_DC_DCLOW.png", plot=p2, device="png",
        height=5, width=5, units="in", dpi=500, path="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/")
#
p2=VlnPlot(cdc, group.by = "severity", "DC2dc1", cols = getPalette(length(unique(cdc$severity))) )
ggsave(filename="VLN_DC_DCLOW_Sev.png", plot=p2, device="png",
        height=5, width=5, units="in", dpi=500, path="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/")
```

Isolate and compare the percentage of Tfh cells within CD4Tcells:
```{r}
tcd4$Tfhstate= ifelse( tcd4$TFHSignature1 > 0, "TFHpos", "TFHneg" )
nc1= as.data.frame.table(table(tcd4$DiseaseGroup, tcd4$Tfhstate))
colnames(nc1)=c("Severity","TfhState","number_cells")
```

```{r}
g=ggplot(nc1, aes(x=Severity, y=number_cells, fill=TfhState)) + 
    geom_bar(position="stack", stat="identity") + rotate_x_text()
ggsave(filename="Barplot_TfhState_Severity.png", plot=g, device="png",
        height=8, width=8, units="in", dpi=500)
```

ISOLATE ONLY TFH positive cells:
```{r}
Idents(tcd4)= "type"
tfhc= subset(tcd4, idents = "TFHpos")
tfhc=preprocess(tfhc)
nc2= as.data.frame(table(tfhc$DiseaseGroup))
colnames(nc2)= c("DiseaseGroup", "Number_TFHCells")
###
blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )
##
p=ggplot(nc2, aes(x="", y=Number_TFHCells, fill=DiseaseGroup)) +
geom_bar(width = 1, stat = "identity")  + coord_polar("y", start=0) +
  blank_theme +
  theme(axis.text.x=element_blank())+
  geom_text(aes( y = Number_TFHCells/7 +c(0, cumsum(Number_TFHCells-30)[-length(Number_TFHCells)]) , 
                label = paste(Number_TFHCells/100, "%")), size=3)
ggsave(filename="Camembert_TFHpos_DG.png", plot=p, device="png",
        height=8, width=8, units="in", dpi=500)
```

```{r}
th1=list(c("IFNG", "TBX21","TNF", "CXCR3"))
th2=list(c( "IL4", "IL5", "GATA3", "IL13"))
th17= list(c("IL17A", "IL17F", "RORC", "CCR6"))
```

```{r}
tfhc= AddModuleScore(tfhc, features = th1, name = "TH1signature", nbin = 100,ctrl= 200) #, 
##
tfhc= AddModuleScore(tfhc, features = th2, name = "TH2signature", nbin = 100,ctrl= 200)
##
tfhc= AddModuleScore(tfhc, features = th17, name = "TH17signature", nbin = 100,ctrl= 200)
```

TFH1:
```{r}
p1=VlnPlot(tfhc, group.by = "sampleID", "TH1signature1", cols = getPalette(length(unique(tfhc$sampleID))) )  +NoLegend()
##
p2=VlnPlot(tfhc, group.by = "DiseaseGroup", "TH1signature1", cols = getPalette(length(unique(tfhc$DiseaseGroup))) ) +NoLegend()
##
p=p1+p2
ggsave(filename="VLN_TFH1DG_SID.png", plot=p, device="png",
        height=10, width=8, units="in", dpi=500)
```

TFH2:
```{r}
p1=VlnPlot(tfhc, group.by = "sampleID", "TH2signature1", cols = getPalette(length(unique(tfhc$sampleID))) )  +NoLegend()
##
p2=VlnPlot(tfhc, group.by = "DiseaseGroup", "TH2signature1", cols = getPalette(length(unique(tfhc$DiseaseGroup))) ) +NoLegend()
##
p=p1+p2
ggsave(filename="VLN_TFH1DG_SID.png", plot=p2, device="png",
        height=10, width=8, units="in", dpi=500)
```

```{r}
p=FeatureScatter(tfhc, "TH2signature1", "TH1signature1", group.by = "DiseaseGroup", cols = getPalette(length(unique(tfhc$DiseaseGroup))) )

ggsave(filename="FS_TFH2_TFH1.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
```

TFH17:
```{r}
p1=VlnPlot(tfhc, group.by = "sampleID", "TH17signature1", cols = getPalette(length(unique(tfhc$sampleID))) )  +NoLegend()
##
p2=VlnPlot(tfhc, group.by = "DiseaseGroup", "TH17signature1", cols = getPalette(length(unique(tfhc$DiseaseGroup))) ) +NoLegend()
##
p=p1+p2
ggsave(filename="VLN_TFH17_DG_SID.png", plot=p, device="png",
        height=10, width=8, units="in", dpi=500)
```
#####
Calculate percentages per severity:
```{r}
which(rownames(as.matrix(tfhc@assays$RNA@data))=="CXCR3")
tfhc$CXCR3= as.matrix(tfhc@assays$RNA@data)[13847,]
which(rownames(as.matrix(tfhc@assays$RNA@data))=="CCR6")
tfhc$CCR6= as.matrix(tfhc@assays$RNA@data)[11741,]

tfhc$TfhSubtype= ifelse(tfhc$TH1signature1>0 & tfhc$CXCR3 > 0.1 & tfhc$CCR6 < 0.1, "Tfh1pos", ifelse(tfhc$TH2signature1 >0 & tfhc$CXCR3 < 0.1 & tfhc$CCR6 < 0.1 , "Tfh2pos", ifelse(tfhc$TH17signature1 >0 & tfhc$CXCR3 < 0.1 & tfhc$CCR6 > 0.1, "Tfh17pos", "TfhOther")))
table(tfhc$TfhSubtype)
```


```{r}
Idents(tfhc)="TfhSubtype"
library(data.table)
nbr=as.data.table(table(tfhc$TfhSubtype ,tfhc$DiseaseGroup), keep.rownames = T)
##
g=ggplot(nbr, aes(x=V1, y=N, fill=V2)) + 
    geom_bar(position="stack", stat="identity") + rotate_x_text()

ggsave(filename="Barplot_TfhStatesAll_DS.png", plot=g, device="png",
        height=8, width=8, units="in", dpi=500)
```

Tfh_Subtype Severity
```{r}
x=table(tfhc$TfhSubtype ,tfhc$sampleID)
nc=colnames(x)
nr=rownames(x)
x=as.matrix.data.frame(x)
colnames(x)=nc
rownames(x)= nr
x=as.data.frame(x)
x=as.data.frame(t(x))
write.csv(x, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/normalizeNbrCells_CountTable_Tfhstates_DG_ALLCORRECT.csv")
##
x2=round(x/table(tfhc$sampleID),2)*100
#write.csv(x2, "CountTable_Tfhstates_DG_PercentagesOfTotalTFH.csv")
write.csv(x2, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/normalizeNbrCells_CountTable_Tfhstates_DG_Percentages.csv")
```

DO THE SAME FOR DC:
```{r}
#cDC=list(c("ANPEP",  "CD1C", "ITGAX", "CST3", "FCER1A"))
#s= AddModuleScore(s, features = cDC, name = "cDC", nbin = 100, ctrl = 200)
cdc=subset(s, subset= CD1C > 0.1 & ANPEP > 0.1 & THBD < 0.1)
cdc=DietSeurat(cdc)
cdc=preprocess(cdc)
##
getPalette = colorRampPalette(brewer.pal(5, "Dark2"))
p1= DimPlot(cdc, group.by = "DiseaseGroup", cols = getPalette(length(unique(cdc$DiseaseGroup))))
##
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Umap_DC_DG.png", plot=p1, device="png",height=5, width=5, units="in", dpi=500)
#
cdc$severity= ifelse(cdc$DiseaseGroup %in% grep("Healthy", cdc$DiseaseGroup, value = T), "HC", ifelse(cdc$DiseaseGroup %in% grep("COVID", cdc$DiseaseGroup, value = T),"Covid","Influenza" ))

getPalette = colorRampPalette(brewer.pal(3, "YlOrRd"))
p2= DimPlot(cdc, group.by = "severity", cols = getPalette(length(unique(cdc$severity))))
##
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Umap_DC_Sev.png", plot=p2, device="png",height=5, width=5, units="in", dpi=500)
```

```{r}
dc1=list(c("ASXL3", "RNF17", "CLUHP3", "SULF1", "ADORA2A", "HNF1B", "MYH7", "SERPINE2", "EDIL3"))
dc2=list(c("CATSPER1", "BCAN","CD302", "FAM81A", "ARHGEF15", "TRIM10", "SNX29P1", "NME1-NME2"))
```

```{r}
cdc= AddModuleScore(cdc, features = dc1, name = "DC1dc", nbin = 100, ctrl = 100)
cdc= AddModuleScore(cdc, features = dc2, name = "DC2dc", nbin = 100, ctrl = 100) #, nbin = 100, ctrl = 200

cdc$DCsubset= ifelse(cdc$DC2dc1 > 0 & cdc$DC1dc1 < 0 , "DClow", 
                     ifelse(cdc$DC1dc1>0 & cdc$DC1dc1 < 0, "DChigh"
                            , "DCother"))
```

```{r}
#xd=table(cdc$DCsubset ,cdc$DiseaseGroup)
#xd=table(cdc$DCsubset ,cdc$severity)
xd=table(cdc$DCsubset ,cdc$sampleID)
a=colnames(xd)
b=rownames(xd)
xd=as.matrix.data.frame(xd)
colnames(xd)=a
rownames(xd)=b
xd=as.data.frame(xd)
xd=as.data.frame(t(xd))
write.csv(xd, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/DCcounts_DG.csv")
##
xdp= round(xd/table(cdc$sampleID),2)*100
write.csv(xdp, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/DCPercentage_SampleID_Normalized.csv")
```
Merge the two: DG:
```{r}
all(rownames(xdp)==rownames(x2))
percentages=cbind(xdp, x2)
#perdata=percentages[,-c(3,7)]
percentages$Tfh= round(table(tfhc$sampleID)/ncol(tcd4),2)*100
##
  write.csv(percentages, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentage_SAMPLEID_tfh_dc_Rounded_Normalized.csv")
```

```{r}
perdata=percentages[,-c(1,7,11)]
write.csv(perdata, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentage_SAMPLEID_tfh_dc_Rounded_Normalized_Cleaned.csv")
  #
dt=as.data.frame(t(perdata))
dt$celltype=rownames(dt)
dt=dt[-c(3,4),]
dt=dt[,-9]
#dt=dt[,-4]
#dt=dt[c(4,2,1,3,5),]
dd= reshape2::melt(dt, "celltype")
p=ggplot(dd, aes(fill=variable, y=value, x=celltype)) + 
    geom_bar(position="dodge", stat="identity") 
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/BaplotPercentages_DG_WithoutHD.png", plot=p, device="png",
        height=8, width=8, units="in", dpi=500)
```

```{r}
p=ggplot(dd, aes(x=variable, y=value, group=celltype, color=celltype)) + 
  geom_line() +
  rotate_x_text(angle=315)+
labs(title="Percentage of cells_Tc_DC", x="Disease_Stage", y = "%Cells")+
   theme_classic() 
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Perc_Cells_DCT_Sev_WithoutHD.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
```

```{r}
xd=table(cdc$sampleID, cdc$DCsubset)
a=colnames(xd)
b=rownames(xd)
xd=as.matrix.data.frame(xd)
colnames(xd)=a
rownames(xd)=b
xd=as.data.frame(xd)
#####
xt=table(tfhc$sampleID, tfhc$TfhSubtype)
a=colnames(xt)
b=rownames(xt)
xt=as.matrix.data.frame(xt)
colnames(xt)=a
rownames(xt)=b
xt=as.data.frame(xt)
##
all(rownames(xt)==rownames(xd))

#pds= cbind(xd, xt)

##
pds=xt
pds= cbind(xd, xt)
##
pds=percentages
rownames(ms1)=ms1$`Sample ID`
ms1$`Sample ID`=gsub(" ", "",ms1$`Sample ID`)
ms1=as.data.frame(ms1)
percentages$sampleID= rownames(percentages)
ms1$`Sample ID`= c(ms1$`Sample ID`[1:16], paste0("HD",seq(1,4)))
all(rownames(percentages)== ms1$`Sample ID`)
percentages=percentages[order(match(percentages$sampleID,ms1$`Sample ID`)),]
pds=percentages
pds$Disease_Group=ms1$`Disease group`
#pds=pds[,-c(3,7)]
#pds=pds[-c(8,9,16),]
##
pds$severity= ifelse(pds$Disease_Group %in% grep("Healthy", pds$Disease_Group, value = T), "HC", ifelse(pds$Disease_Group %in% grep("COVID", pds$Disease_Group, value = T),"Covid","Influenza" ))

write.csv(pds, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/PDS_TrueValuesperSample.csv")
```

```{r}
#Tfh1:
t1=pds[,c(10,13)]
dds= reshape2::melt(t1, "Disease_Group")
####
p3 <- ggplot(dds, aes(x=Disease_Group, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of cells_Tfh1", x="Disease_Group", y = "%Cells")+
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "Healthy donor")+theme_classic() 

ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_Tfh1_dots_Severity_SAMPLEID.png", plot=p3, device="png",
        height=5, width=5, units="in", dpi=500)
```

```{r}
#Tfh1:
t1=pds[,c(4,13)]
dds= reshape2::melt(t1, "Disease_Group")
####
p3 <- ggplot(dds, aes(x=Disease_Group, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of cells_Tfh1", x="Disease_Group", y = "%Cells")+

   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "mild COVID-19")+
   theme_classic() 

ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_Tfh1_dotsSampleID.png", plot=p3, device="png",
        height=5, width=5, units="in", dpi=500)
```

DClow:
```{r}
t1=pds[,c(6,14)]
dds= reshape2::melt(t1, "severity")

p <- ggplot(dds, aes(x=severity, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of DClow", x="Disease_Group", y = "%Cells")+
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "HC")+
   theme_classic() 
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_DClow_dotsSev_SampleID.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
```

DCHIGH
```{r}
pds$DChigh=rep(2,nrow(pds))
t1=pds[,c(8,13)]
dds= reshape2::melt(t1, "Disease_Group")

p <- ggplot(dds, aes(x=Disease_Group, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of Tfh17", x="Disease_Group", y = "%Cells")+
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "mild COVID-19")+
   theme_classic() 
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_DCHigh_dotsSEV.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
```

```{r}
p=DimPlot(cdc, group.by = "DCsubset")
ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/DC_UMAP.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
```

TFH2:
```{r}
t1=pds[,c(10,13)]
dds= reshape2::melt(t1, "Disease_Group")

p2 <- ggplot(dds, aes(x=Disease_Group, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of tfh2", x="severity", y = "%Cells")+
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "mild COVID-19")   +
   theme_classic() 

ggsave(filename="/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_Tfh2_dotsSev_SAMPLEID_DG.png", plot=p2, device="png",
        height=5, width=5, units="in", dpi=500)
```

TFH17:
```{r}
t1=pds[,c(3,8)]
dds= reshape2::melt(t1, "severity")
#
p2 <- ggplot(dds, aes(x=severity, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of tfh17", x="Disease_Group", y = "%Cells")+
   stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "HC")  +
   theme_classic() 

ggsave(filename="Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_TFH17_dotsSev.png", plot=p2, device="png", height=5, width=5, units="in", dpi=500)
```
TFH17:
```{r}
t1=pds[,c(1,6)]
dds= reshape2::melt(t1, "Disease_Group")
#
p2 <- ggplot(dds, aes(x=Disease_Group, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of DHhigh", x="Disease_Group", y = "%Cells")+
  stat_compare_means(label = "p.signif", method = "wilcox.test", ref.group = "mild COVID")   +
   theme_classic() 
ggsave(filename="Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/Percentages_DChigh_dots.png", plot=p2, device="png",
        height=5, width=5, units="in", dpi=500)
```

```{r}
Tfhpos=as.vector(table(tfhc$sampleID))/ncol(tcd4)
pds=cbind(Tfhpos, pds)
##
t1=pds[,c(1,7)]
dds= reshape2::melt(t1, "Disease_Group")
#
p2 <- ggplot(dds, aes(x=Disease_Group, y=value)) + 
    geom_dotplot(binaxis='y', stackdir='center') +
 stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  rotate_x_text(angle=90) +
labs(title="Percentage of Tfh", x="Disease_Group", y = "%Cells")+
   theme_classic() 
ggsave(filename="Percentages_Tfh_dots.png", plot=p2, device="png",
        height=5, width=5, units="in", dpi=500)
```

Take the same number of TFH positive and DClow positive cells and try to do correlation:
```{r}
table(cdc$DCsubset) # take 284 cells
table(tfhc$Tfhstate) #1019 POSITIVE CELLS; from which 291 are TFH1positive
###

###
ms=pds[which(pds$Disease_Group %in% c("mild COVID", "severe COVID")),]
ms[,-7]= ms[,-7]*100

sp <- ggscatter(ms, x = "DClow", y = "Tfh1pos",
                add = "reg.line",               # Add regression line
                conf.int = F,                # Add confidence interval
                color = "Disease_Group", palette = "jco", # Color by groups "cyl"
                shape = "Disease_Group")+
  stat_cor(aes(color = Disease_Group), label.x = 1.13, label.y = 5.2) 
```

```{r}
d1=as.data.frame(tfh1p$TH1signature1, col.names=c("Tfh1"))
d1$sid=tfh1p$sampleID
```

```{r}
saveRDS(cdc,"/Users/equipe.soumelis/Desktop/COVID-19_TFH1/cdc.Rds")
saveRDS(tfhc,"/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Tfh.Rds")
saveRDS(pds,"/Users/equipe.soumelis/Desktop/COVID-19_TFH1/PDS.Rds")
```
########

```{r}
p1=DimPlot(tcd4, group.by = "DiseaseGroup",  cols = getPalette(length(unique(tcd4$DiseaseGroup))))
##
p2=DimPlot(cdc, group.by = "DiseaseGroup",  cols = getPalette(length(unique(cdc$DiseaseGroup))))
p=p1+p2

ggsave(filename="Umap_CD4_DC.png", plot=p, device="png",
        height=5, width=10, units="in", dpi=500)
##
p3=DimPlot(tcd4, group.by = "Tfhstate", cols = c("grey", "red"))
ggsave(filename="Umap_CD4_TFHpos.png", plot=p3, device="png",
        height=5, width=5, units="in", dpi=500)
```

WHY so different clusters:
```{r}
Idents(tcd4)="seurat_clusters"
cm= FindMarkers(tcd4, ident.1 = c(9,8,2), ident.2 = NULL, only.pos = F, logfc.threshold = 0.5) 
```

```{r}
library(RColorBrewer)
library(ggpubr)
p=DimPlot(tfhc, group.by = "TfhSubtype",cols= getPalette(length(unique(tfhc$TfhSubtype))))
ggsave(filename="Umap_TFHpos_TFHsubsets.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
##
brewer.pal.info
getPalette = colorRampPalette(brewer.pal(4, "Dark2"))
p=DimPlot(cdc, group.by = "DCsubset",cols= getPalette(length(unique(cdc$DCsubset))))
ggsave(filename="Umap_cDCsubsets.png", plot=p, device="png",
        height=5, width=5, units="in", dpi=500)
```

```{r}
th1=list(c("IFNG", "TBX21","TNF"))
th2=list(c( "IL4", "IL5", "GATA3"))
th17= list(c("IL17A", "IL17F", "RORC"))
```

```{r}
Idents(tcd4)="Tfhstate"
tfhn= subset(tcd4, idents = "TFHneg")
tfhn=DietSeurat(tfhn)
tfhn=preprocess(tfhn)
##
tfhn= AddModuleScore(tfhn, features = th1, name = "TH1signature", nbin = 100,ctrl= 100) #, 
tfhn= AddModuleScore(tfhn, features = th2, name = "TH2signature", nbin = 100,ctrl= 100)
tfhn= AddModuleScore(tfhn, features = th17, name = "TH17signature", nbin = 100,ctrl= 100)
#
tfhn$TfSubtype= ifelse(tfhn$TH1signature1>0.1, "Th1pos", ifelse(tfhn$TH2signature1 >0.2, "Th2pos", ifelse(tfhn$TH17signature1 >0.1, "Th17pos", "ThOther")))
table(tfhn$TfSubtype)
```

```{r}
mono=list(c("CD14", "FCGR1A"," S100A12", "FCGR3A", "MS4A7", "LYZ", "CXCR3"))
s=AddModuleScore(s, features = mono, name = "monocytesignature", nbin = 100,ctrl= 100)
monocyte= subset (s, monocytesignature1 >0)
##
monocyte=subset(monocyte, FCGR3A > 0.5)
monocyte=DietSeurat(monocyte)
monocyte= preprocess(monocyte)
##
x=table(monocyte$DiseaseGroup)/ncol(monocyte)
m=colnames(x)
n=rownames(x)
x=as.matrix.data.frame(x)
colnames(x)=m
rownames(x)= n
x=as.data.frame(x)
x=as.data.frame(t(x))
write.csv(x, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/CountTable_Tfhstates_DG_ALLCORRECT.csv")
##
x2=x/ncol(tfhc)
```

```{r}
table( s$DiseaseGroup)
```

```{r}
B=list(c("CD19", "MS4A1", "CD79A", "CD79B"))
s=AddModuleScore(s, features = B, name = "bsignature", nbin = 100,ctrl= 100)
bc=subset(s, bsignature1 > 0.2)
table(bc$DiseaseGroup)/ncol(bc)
```

```{r}
tfhc$orig.ident="tfh"
cdc$orig.ident="cdc"
dat=merge(tfhc, cdc)
dat=preprocess(dat)
dt= table(dat$DC2dc1, dat$TFH1signature1) %>% as.data.frame()

dt=as.data.frame(dt)
rownames(dt)=n
```
```{r}
saveRDS(cdc,"/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/CDC.Rds" )
saveRDS(pds,"/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/PercentagesDC_TFH.Rds" )
saveRDS(tcd4, "/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/TCD4.Rds")
saveRDS(tfhc,"/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/TFH.Rds")
pds= readRDS("/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/PercentagesDC_TFH.Rds")
tfhc=readRDS("/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/TFH.Rds")
cdc=readRDS("/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/CDC.Rds")
tcd4=readRDS("/Users/equipe.soumelis/Desktop/COVID-19_TFH1/Analysis_19nov/TCD4.Rds")
```

calculate the percentages:
```{r}

```

